### Exercises (Chapter 5)

```{r}
#| include: false
library(tidyverse)
library(nycflights13)
```


::: {.callout-tip icon="false" title="Tables"}
```{r}
table1
table2
table3
```
:::


1.  For each of the sample tables, describe what each observation and each column represents.

    ::: {.callout-note icon="false" title="Answer"}
    *Your text answer here.*
    :::

2.  Sketch out the process you'd use to calculate the `rate` for `table2` and `table3`. You will need to perform four operations:

    a.  Extract the number of TB cases per country per year.
    b.  Extract the matching population per country per year.
    c.  Divide cases by population, and multiply by 10000.
    d.  Store back in the appropriate place.

    You haven't yet learned all the functions you'd need to actually perform these operations, but you should still be able to think through the transformations you'd need.
    
    
    ::: {.callout-note icon="false" title="Answer"}
    ```{r}
    table2 |>
      pivot_wider(names_from = type,
                  values_from = count) |>
      mutate(rate = cases / population * 10000)
    #
    table3 |>
      separate_wider_delim(
        cols = rate,
        delim = "/",
        names = c("cases", "population"),
      ) |>
      mutate(
        cases = as.numeric(cases),
        population = as.numeric(population),
        rate = cases / population * 10000
      )
    ```
    For `table2`, we need to reshape the data to have a column for cases and a column for population and then divide the two to calculate the rate. A possible approach is shown above.
    
    For `table3,` we need to separate cases and population into their own columns and then divide them. A possible approach is shown above.
    :::
