### Exercises (Chapter 7)

```{r}
#| include: false
library(tidyverse)
```


1.  What function would you use to read a file where fields were separated with "\|"?

    ::: {.callout-note icon="false" title="Answer"}
    *Your text answer here.*
    :::

2.  Apart from `file`, `skip`, and `comment`, what other arguments do `read_csv()` and `read_tsv()` have in common?

    ::: {.callout-note icon="false" title="Answer"}
    *Your text answer here.*
    :::

3.  What are the most important arguments to `read_fwf()`?

    ::: {.callout-note icon="false" title="Answer"}
    *Your text answer here.*
    :::

4.  Sometimes strings in a CSV file contain commas. To prevent them from causing problems, they need to be surrounded by a quoting character, like `"` or `'`. By default, `read_csv()` assumes that the quoting character will be `"`. To read the following text into a data frame, what argument to `read_csv()` do you need to specify?

    ```{r}
    #| eval: false

    "x,y\n1,'a,b'"
    ```
    
    ::: {.callout-note icon="false" title="Answer"}
    We need to specify the `quote` argument.
    ```{r}
    read_csv("x,y\n1,'a,b'", quote = "\'")
    ```
    
    :::

5.  Identify what is wrong with each of the following inline CSV files. What happens when you run the code?

    ```{r}
    #| eval: false

    read_csv("a,b\n1,2,3\n4,5,6")
    read_csv("a,b,c\n1,2\n1,2,3,4")
    read_csv("a,b\n\"1")
    read_csv("a,b\n1,2\na,b")
    read_csv("a;b\n1;3")
    ```
    
    ::: {.callout-note icon="false" title="Answer"}
    ```{r}
    read_csv("a,b\n1,2,3\n4,5,6")
    ```
    There are only two column headers but three values in each row, so the last two get merged.
    :::
    
    ::: {.callout-note icon="false" title="Answer"}
    ```{r}
    read_csv("a,b,c\n1,2\n1,2,3,4")
    ```
    here are only three column headers, first row is missing a value in the last column so gets an NA there, the second row has four values so the last two get merge
    :::
    
    ::: {.callout-note icon="false" title="Answer"}
    ```{r}
    read_csv("a,b\n\"1")
    ```
    No rows are read in.
    :::
    
    ::: {.callout-note icon="false" title="Answer"}
    ```{r}
    read_csv("a,b\n1,2\na,b")
    ```
    Each column has a numerical and a character value, so the column type is coerced to character.
    :::
    
    ::: {.callout-note icon="false" title="Answer"}
    ```{r}
    read_csv("a;b\n1;3")
    ```
    The delimiter is `;` but it’s not specified, therefore this is read in as a single-column data frame with a single observation.
    :::
    
    

6.  Practice referring to non-syntactic names in the following data frame by:

    ```{r}
    set.seed(321)
    annoying <- tibble(
      `1` = 1:10,
      `2` = `1` * 2 + rnorm(length(`1`))
    )
    ```

    a.  Extracting the variable called `1`.
    
        ::: {.callout-note icon="false" title="Answer"}
        ```{r}
        annoying |> 
          select(`1`)
        # or
        annoying$`1`
        ```
    
        :::
    
    b.  Plotting a scatterplot of `1` vs. `2`.
    
        ::: {.callout-note icon="false" title="Answer"}
        ```{r}
        annoying |> 
          ggplot(aes(x = `2`, y = `1`)) + 
            geom_point()
        ```
    
        :::
    c.  Creating a new column called `3`, which is `2` divided by `1`.
    
        ::: {.callout-note icon="false" title="Answer"}
        ```{r}
        annoying |> 
          mutate(`3` = `2`/`1`)
        ```
    
        :::
    
    d.  Renaming the columns to `one`, `two`, and `three`.

        ::: {.callout-note icon="false" title="Answer"}
        ```{r}
        annoying |> 
          mutate(`3` = `2`/`1`) |> 
            rename(
            "one" = `1`,
            "two" = `2`,
            "three" = `3`
            )
        ```
    
        :::

    